\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2021-08-20 paper.tex
Update the definition of Sigma_i
Update matrix formulation

\texttt{TODO Van Tuan : define $\Sigma_i$}

@@

Let us introduce the following useful notations
\begin{equation}
  \label{eq:g-tilde}
  \left\{
    \begin{array}{ll}
    \tilde g^1&: b_i \mapsto b_i,\\
    \tilde g^2&: b_i \mapsto b_ib_i^\top, \\
    \tilde g^3_{s}&: b_i \mapsto \Psi_i(s), \\
    \tilde g^4_{s, \gamma_k}&: b_i \mapsto \exp \big\{\gamma_k^\top g^3_{s}(b_i) \big\}, \\
    \tilde g^5_{s, \gamma_k}&: b_i \mapsto g^3_{s}(b_i)^\top g^4_{s}(b_i).
    \end{array}
  \right. 
\end{equation}
We also denote 
\[ \cI_1 = 
\begin{bmatrix}
  \ind{\{t_{1} = t_1^u\}}  & \cdots & \ind{\{t_{1} = t_J^u\}}\\
  \vdots &  \ddots & \vdots \\
  \ind{\{t_{n} = t_1^u\}} & \cdots & \ind{\{t_{n} = t_J^u\}}
\end{bmatrix}
\in \R^{n \times J}
\quad \text{and} \quad 
\cI_2 = 
\begin{bmatrix}
  \ind{\{t_{1} \leq t_1^u\}} & \cdots & \ind{\{t_{1} \leq t_J^u\}}\\
  \vdots &  \ddots & \vdots \\
  \ind{\{t_{n} \leq t_1^u\}} & \cdots & \ind{\{t_{n} \leq t_J^u\}}
\end{bmatrix}
\in \R^{n \times J} \]
some matrices to compare each event times with the vector of distinct event times. Those matrices are widely used in practice to replace indicators. For instance
\begin{align*}
f(t_i, \delta_i| b_i, G_i = k ; \theta) &= \Big( \sum_{j=1}^J \lambda_0(t_j) \tilde g_{i, t_j, \gamma_k^, \beta_k}^1 \ind{\{t_j = t_i\}} \Big)^{\delta_i} \exp \Big( - \sum_{j=1}^J \lambda_0(t_j) \tilde g_{i, t_j, \gamma_k, \beta_k}^1 \ind{\{t_j \leq t_i\}} \Big) \\
& = \Big( \text{sum}(\mathbf{\lambda_0} \tilde g_{\gamma_k, \beta_k}^1 \cI_1) \Big)^{\delta_i} \exp \Big( - \text{sum} (\mathbf{\lambda_0} \tilde g_{\gamma_k, \beta_k}^1\cI_2) \Big)
\end{align*}

\texttt{TODO Van Tuan : rewrite the two previous lines addind the $^{(w)}$ (else it's not true ! since it's only ok for the estimator) + the rigth $\tilde g$ + introduce undefined notations.}

>>>>

\noindent where $\Sigma_i$ is a diagonal matrix whose diagonal is $\Phi_i$.

@@

Let us introduce the following useful notations
\begin{equation}
  \label{eq:g-tilde}
  \left\{
    \begin{array}{ll}
    \tilde g^1&: b_i \mapsto b_i,\\
    \tilde g^2&: b_i \mapsto b_ib_i^\top, \\
    \tilde g^3_{s}&: b_i \mapsto \Psi_i(s), \\
    \tilde g^4_{s, \gamma_k}&: b_i \mapsto \exp \big\{\gamma_k^\top g^3_{s}(b_i) \big\}, \\
    \tilde g^5_{s, \gamma_k}&: b_i \mapsto g^3_{s}(b_i)^\top g^4_{s}(b_i).
    \end{array}
  \right. 
\end{equation}
We also denote 
\[ \cI_1 = 
\begin{bmatrix}
  \ind{\{t_{1} = t_1^u\}}  & \cdots & \ind{\{t_{1} = t_J^u\}}\\
  \vdots &  \ddots & \vdots \\
  \ind{\{t_{n} = t_1^u\}} & \cdots & \ind{\{t_{n} = t_J^u\}}
\end{bmatrix}
\in \R^{n \times J}
\quad \text{and} \quad 
\cI_2 = 
\begin{bmatrix}
  \ind{\{t_{1} \leq t_1^u\}} & \cdots & \ind{\{t_{1} \leq t_J^u\}}\\
  \vdots &  \ddots & \vdots \\
  \ind{\{t_{n} \leq t_1^u\}} & \cdots & \ind{\{t_{n} \leq t_J^u\}}
\end{bmatrix}
\in \R^{n \times J} \]
some matrices to compare each event times with the vector of distinct event times. Those matrices are widely used in practice to replace indicators. For instance
\begin{align*}
f(t_i, \delta_i| b_i, G_i = k ; \theta^{(w)}) &= \big[\lambda_0^{(w)}(t_i) \exp \big\{{\gamma_k^{(w)}}^\top\Psi_i(t_i) \big\} \big]^{\delta_i} \exp \Big( - \sum_{j=1}^{J-1} (t_{j+1}^u-t_j^u) \lambda_0^{(w)}(t_j^u) \exp \big\{{\gamma_k^{(w)}}^\top \Psi_i(t_j^u)\big\} \ind{\{t_j^u < t_i\}} \Big) \\
& = \big[\lambda_0^{(w)}(t_i) g^4_{t_i, \gamma_k}(b_i) \big]^{\delta_i} \exp \Big( - \sum_{j=1}^{J-1} (t_{j+1}^u-t_j^u) \lambda_0^{(w)}(t_j^u) g^4_{t_j^u, \gamma_k}(b_i) \ind{\{t_j^u < t_i\}} \Big)
\end{align*}

\texttt{TODO Van Tuan : update matrix formulation.}
